Reproducible Summary Tables with gtsummary

### 2020-12-09 RJtemplate_gtsummary_submission.tex
Updates from Overleaf

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\hypertarget{data-summaries}{%
\section{Data Summaries}\label{data-summaries}}

@@

>>>>

\section{Introduction}

\section{Data Summaries}

@@

\subsection{\texorpdfstring{\texttt{tbl\_summary()}}{tbl\_summary()}}

% code for basic tbl_summary()
\begin{example}
tbl_summary_1 <-
  trial %>%
  select(age, grade, response, trt) %>%
  tbl_summary(by = trt)
\end{example}

\subsection{\texorpdfstring{\texttt{tbl\_svysummary()}}{tbl\_svysummary()}}

\subsection{\texorpdfstring{\texttt{tbl\_cross()}}{tbl\_cross()}}

\subsection{\texorpdfstring{\texttt{tbl\_survfit()}}{tbl\_survfit()}}

\subsection{Customization}

\section{Model Summaries}

\subsection{\texorpdfstring{\texttt{tbl\_regression()}}{tbl\_regression()}}

\hypertarget{tbl_uvregression}{%
\subsection{\texorpdfstring{\texttt{tbl\_uvregression()}}{tbl\_uvregression()}}\label{tbl_uvregression}}

\hypertarget{in-line-reporting}{%
\section{In-line Reporting}\label{in-line-reporting}}

\hypertarget{merging-and-stacking}{%
\section{Merging and Stacking}\label{merging-and-stacking}}

\hypertarget{themes}{%
\section{Themes}\label{themes}}

\hypertarget{print-engines}{%
\section{Print Engines}\label{print-engines}}
